Parallel Adaptive Importance Sampling

### 2015-08-14 PAIS.tex
updated adaptive algorithm description

When implemented, there are a number of parameters which must be
chosen to allow efficient tuning of $\delta$. Firstly, the initial
value of $\delta$ should be chosen so that the chains spread out
quickly across the state space. However, if it is chosen to be too
large, then the method may become unstable and inefficient.

>>>>

When implemented, there are a number of parameters which must be
chosen to allow efficient tuning of $\delta$. Firstly, the initial
value of $\delta$ should be chosen so that the chains spread out
quickly across the state space. However, if it is chosen to be too
large, then the method may become unstable and inefficient. We also choose two iteration numbers at which we change our adaptive strategy. At iteration $N_\text{join}$ we resample using the full ensemble size instead of using to subsets of the full ensemble. This allows us to fine-tune the scaling parameter using the full resampler, but slows down the rate of convergence of the scaling parameter. Finally we choose a time, $N_\text{stop}$, at which we stop updating our parameter to guarantee ergodicity of the MCMC algorithm.
